%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Digital Video Application Laboratory (Federal University of Paraíba)} % Organization
    {João Pessoa, Brazil} % Location
    {Oct. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of a team for software development of a video application for Digital TV, sponsored by the Brazilian Ministry of Culture, including a backend application and website.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Professor} % Job title
    {Motiva/Federal University of Campina Grande} % Organization
    {João Pessoa, Brazil} % Location
    {Mar. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programming professor of children between 10 and 14 years old, focusing in competitive programming.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Digital Signal Processing Group (Federal Institute of Education, Science and Technology of Paraíba)} % Organization
    {João Pessoa, Brazil} % Location
    {Jul. 2015 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Research and software development of a body measurement application.}
        \item {Implemented a software for body measurement in C++ and OpenCV.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Summer Research Intern} % Job title
    {NICTA (National ICT Australia)} % Organization
    {Sydney, Australia} % Location
    {Nov. 2014 - Feb. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research assistant crawling information from HTTP request dataset.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Digital Signal Processing Group (Federal Institute of Education, Science and Technology of Paraíba)} % Organization
    {João Pessoa, Brazil} % Location
    {Jul. 2013 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Research in metrics for 2D and 3D videos.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
