%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Member, Volunteer, Secretary, Vice-Chairperson \& Chairperson} % Affiliation/role
    {IFPB IEEE Student Branch} % Organization/group
    {João Pessoa, Brazil} % Location
    {Dec. 2012 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
		\item{Development in leadership, communication, verbal, adversities solution skills and other soft skills.}
		\item{Gained expertise in organizing events and writing reports.}
		\item{Increased technical skills doing undergraduate researches.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Competitor Member \& Staff} % Affiliation/role
    {IFPB Olympic Programming Project (POP)} % Organization/group
    {João Pessoa, Brazil} % Location
    {Ago. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participation in problem solving competition, obtaining good awards.}
        \item {Gained expertise in organizing problem solving competitions.}
      \end{cvitems}
    } 

%---------------------------------------------------------
  \cventry
    {Programming Techniques Course Tutor} % Affiliation/role
    {Federal Institute of Education, Science and Technology of Paraíba} % Organization/group
    {João Pessoa, Brazil} % Location
    {Mar. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained experience in teaching and development of verbal skills.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Volunteer} % Affiliation/role
    {IFPB ACM Student Chapter} % Organization/group
    {Brazil} % Location
    {Jun. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participation in the opening procedure of  the first Brazilian ACM Student Chapter.}
        \item {Development of soft skills.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Member \& Volunteer} % Affiliation/role
    {IFPB IEEE WIE Affinity Group} % Organization/group
    {João Pessoa, Brazil} % Location
    {Feb. 2013 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
		\item{Gained expertise in engaging women for STEAM fields.}
		\item{Gained experience in developing social inclusion activities.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Programing Logic and Algorithms Course Tutor} % Affiliation/role
    {Federal Institute of Education, Science and Technology of Paraíba} % Organization/group
    {João Pessoa, Brazil} % Location
    {Ago. 2013 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained experience in teaching and development of verbal skills.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
